---
title: "Information Integration Project"
author: "Clement Peters"
date: "5/1/2021"
output: html_document
---

#What do I need to do:

1. Define Agents
  1.1 What types. Agents + info-bits
  1.2 What parameters do they have
    1.2.1 *Agents*
        Memory
            How large is memory? Parameter*
        Location in attitude space (xy coordinate)
            This is the mean of the attitudes they hold in memory
            I can make a parameter specifying how closely to the middle the population               will start
    1.2.2 *Info bit*
        Lifespan
            Should be one tick. If they are not integrated they disappear
        Location in attitude space
            Should be random, with a distribution of -1 to 1 on both axis. This will
            represent central information output. Could also be programmed with a                   certain bias, which might represent central information better.
        Trustworthiness score
            How trustworthy is the information perceived generally?
  1.3 What will they do each tick?
    1.3.1 Agents will try to integrate the infobit which is created. Success will depend
        on the information integration formula which gives a probability of being inte-
        grated. *If the info-bit is integrated, they will move closer to that info-bit in         attitude space by averaging and updating their memory*
    1.3.2 If social media is turned on, then the agents will have a probability to share
          their location in attitude space for others to integrate
    1.3.3 Info bits will disappear after one tick
    1.3.4
        
      
 
```{r}
##Packages
pacman::p_load(tidyverse, stringr, dplyr)
```
 
        
  
#d=√((x2−x1)^2+(y2−y1)^2) the distance between two points
# f(d;D,δ) = D^δ/(d^δ+D^δ) Integration formula
  
```{r}
D <- 0.5 #What should the max latitude be when the maximum distance in the attitude space can only be 2.83. It is realistic that a piece of information has 0.5 chance of being integrated, when it's theoretically as far away from the agent as possible? 
d <- 0.5
sharp <- 20
#Max distance?
# x1 <- -1
# y1 <- -1
# 
# x2 <- 1
# y2 <- 1
# sqrt( ((x2-x1)^2)+((y2-y1)^2)) # = 2.828427

D^sharp/(d^sharp+D^sharp)
nMemo <- 10
nPop <- 10

#Define Agents
GenPop <- function(nPop, nMemo, Lat_accept, Sharpness, nGroups){
  

Agent <- data.frame(AgentNo = 1:nPop, # agent number
                    x = 0, # y coordinate
                    y = 0, # x coordinate
                    Lat = Lat_accept, #latitude of acceptance
                    Sharpness = Sharpness,
                    Empty1 = "Empty1",
                    Empty2 = "Empty2",
                    stringsAsFactors = FALSE)

#Assigning each agent to a group
groups <- as.data.frame(matrix(0, nrow = nrow(Agent), ncol = 1))
groups <- rename(groups, Group = V1)

for(a in 1:nrow(groups)){
  
  #It's debatable whether there should be an equal amount of members in each group, or if it should be random. I'm going to start with random amounts (but roughly equal), but later I might change in to be able to control group dynamics.
  groups[a,] <- sample(LETTERS[1:nGroups], 1, replace = TRUE)
}

#Deciding a "sharing threshold" for each agent
sharing <- as.data.frame(matrix(0, nrow = nrow(Agent), ncol = 1))
sharing <- rename(sharing, Share = V1)

for(a in 1:nrow(groups)){
  
  #Each agent will have a value indicating how likely they are to share their point of     view to other agents of their group
  sharing[a,] <- runif(1, 0, 1)
}

#Building memory as dataframe with nMemo*2 column (x & y coordinates)
memory <- as.data.frame(matrix(0, nrow = nrow(Agent), ncol = nMemo*2))

prefixX <- "memory x"
prefixY <- "memory y"
suffix <- seq(1:nMemo)

namesx <- paste(prefixX, suffix, sep = "")
namesy <- paste(prefixY, suffix, sep = "")


colnames(memory)[seq(1,ncol(memory),2)] <- c(namesx)
colnames(memory)[seq(2,ncol(memory),2)] <- c(namesy)

Agent <- cbind(Agent, sharing, groups, memory)
 
return(Agent) 
  }

          


Agents <- GenPop(nPop = 100, nMemo = 10, Lat_accept = 0.3, Sharpness = 4, nGroups = 5)
Agents %>% 
  count(Group, sort = T)

Info <- data.frame(xi = 0.5, # x coordinate for info
                   yi = 0.3, # y coordinate for info
                   Trust = 0, # Trustworthiness score Parameter*
                   TimeExist = 0) 

#Where do the agents start the simulation (default (0,0))
Agents[,2] <- runif(nrow(Agents), -1, 1) #Random x coordinates
Agents[,3] <- runif(nrow(Agents), -1, 1) #Random y coordinates

Iterations <- 1000


ABM1 <- function(Iterations, Plot_freq, Bias){

  #Loop through time
  for(t in 1:Iterations){
    
    #You could argue that the (mainstream) information should have a biased distribution      since the attitudinal space represents a certain topic, and mainstream media is         unlikely to widely change its opinion of it.
    if(Bias == "Neutral"){
    
    
    #Creating neutral information
    Info$xi[1] <- runif(1, -1, 1) #positive bias
    Info$yi[1] <- runif(1, -1, 1) #Positive bias
    
    }
  
   #Conditional statement for Bias
    if(Bias == "Positive"){
    
    
    #Creating biased information
    Info$xi[1] <- rnorm(1, 0.5, 1) #positive bias
    Info$yi[1] <- rnorm(1, 0.5, 1) #Positive bias
    
    #keeping the values between -1 and 1
    while(Info$xi < -1 | Info$xi > 1 & Info$yi < -1 | Info$yi > 1){ 
    Info$xi[1] <- rnorm(1, 0.5, 1) #positive bias
    Info$yi[1] <- rnorm(1, 0.5, 1) #Positive bias
    
    }
  }
    
    if(Bias == "Negative"){
    #You could argue that the (mainstream) information should have a biased distribution      since the attitudinal space represents a certain topic, and mainstream media is         unlikely to widely change its opinion of it.
    
    #Creating biased information
    Info$xi[1] <- rnorm(1, -0.5, 1) #positive bias
    Info$yi[1] <- rnorm(1, -0.5, 1) #Positive bias
    
    #keeping the values between -1 and 1
    while(Info$xi < -1 | Info$xi > 1 & Info$yi < -1 | Info$yi > 1){ 
    Info$xi[1] <- rnorm(1, -0.5, 1) #positive bias
    Info$yi[1] <- rnorm(1, -0.5, 1) #Positive bias
    
    }
  }
  
    
    #Loop through population
    for(i in 1:nrow(Agents)){
    
      #Find the acceptance latitude of agent
      Latitude <- Agents$Lat[i]
      
      #Find attitude sharpness of agent
      Sharpness <- Agents$Sharpness[i]
      
      # Present information to agent:
      
      #which information will the agent meet
      Info_meet <- Info[1,]
      
      #What is the distance between agent and info
      Distance <- sqrt( ((Agents$x[i] - Info$xi)^2)+ ((Agents$y[i] - Info$yi)^2) )
      
      #What is the trustworthiness of info
      Trust <- Info$Trust[1]
      
      #What is the chance they they will integrate
      RandNum <- runif(1,0,1)
      if (RandNum < Latitude^Sharpness/(Distance^Sharpness+Latitude^Sharpness)){
        
        # #If true, check if memory is full
         for(j in 10:ncol(Agents)){
        
        #Check if memory slot is open
         if(Agents[i,j] == 0){
        
           #If true, save the information to the empty memory space
           Agents[i,j] <- Info$xi
           Agents[i,(j+1)] <- Info$yi
           
           #Break out of loop and continue to next agent
           break
  
         }
        }
  
        #If full, sample memory space, and replace with new value (integrate)
        
        #which place in memory should the new info go
        
        #Sample which memory should be replaced. There are nMemo possible values
        sample_num <- as.character(sample(1:((ncol(Agents)-9)/2), size=1)) 
        
        
        #Now i have the location (sample_num), I just need to plot in the new                   information
        colnames_df <- colnames(Agents[i,])
       
        memory_to_replace <- as.data.frame(str_detect(colnames_df, sample_num))
        
        #Now I know the columns in which the new info should go. So I need to put it there
        column <- numeric()
        for(k in 1:nrow(memory_to_replace)){
          if(memory_to_replace[k,] == TRUE){
            
            column <- c(column, k) # Saving the index of the columns
            column <- as.list(column)
            
          }
        }
        x_coord <- column[[1]] # memory x coordinate column number
        y_coord <- column[[2]] # memory y coordinate column number
        
        #To delete the memory I first have to subtract its value from the overall               coordinate, otherwise they will accumulate
        # Agents$x[i] <- Agents$x[i] - Agents[i, x_coord]
        # Agents$y[i] <- Agents$y[i] - Agents[i, y_coord]
        
        #Reset agent position to 0 before updating memory
        Agents$x[i] <- 0
        Agents$y[i] <- 0
        
        # And now we save the new memory in the right location
        Agents[i,][,x_coord] <- Info$xi
        Agents[i,][,y_coord] <- Info$yi
        
        #Now memory is updated. Time to update location on attitude space
        
        #Because the location of the agent is dependent on its memory, it will always be zero to begin with because almost all memories are "neutral". I need to average only over the non-zero memories.
        
        #Number of non-zero columns per agent
        nonZero <- sum(apply(Agents[1,], 2, function(c)sum(c!=0)))
        
        # Averaging the x-values over the number of memories (of value x)
        Agents$x[i] <- sum(Agents[i,seq(10, ncol(Agents), 2)])/((nonZero-7)/2) # -7 because there are always those 3 non memory columns which are nonZero.
        
        # Averaging the y-values over the number of memories (of value y)
        Agents$y[i] <- sum(Agents[i,seq(11, ncol(Agents), 2)])/((nonZero-7)/2) 
        
        }
    }
    
    if(t %% Plot_freq == 0 | t == 1){
    #Visualization:
    
    plot <- Agents %>%
    ggplot(aes(x, y)) + geom_jitter() + xlim(-1, 1) + ylim(-1, 1)
  
     print(plot)
    }
     
  }
  return(Agents)
}

Out1 <- ABM1(1000, 15, Bias = "Neutral")
mean(Out1$x)
sd(Out1$x)
sd(Out1$y)


#For tomorrow: 
# 1. Find a way to model trustworthiness of information, 
# 2. figure out how Lorenz used information popularity, 
# 3. find a way to turn on social media, 
# 4. play with distributions of information valence (more likely positive/negative), 
# 5. see if I can visually see the confirmation bias that is modeled into the integration theory
# 6. Output??? Mean + sd of location over time?



```
  
 
```{r}



```
 
 